\pkg{disaggregation}: An \proglang{R} Package for Bayesian Spatial Disaggregation Modelling

### 2020-02-25 article.Rnw
Tiny reword

%
<<kintroptions, echo=FALSE>>=
knitr::knit_hooks$set(render_sweave())
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  fig.width = 6,
  fig.height = 4,
  fig.pos = 'H',
  prompt=TRUE
)
options(replace.assign=TRUE, width=90, prompt="R> ")
@
%

@@

The \pkg{disaggregation} package contains a C++ function that defines the model and computes the joint likelihood as a function of the parameters and the random effects, in the format expected by \pkg{TMB}. The \pkg{TMB} package then calculates estimates of both parameters and random effects using the Laplace approximation for the likelihood. Evaluation of the objective function and its derivatives is performed via \proglang{R}.

>>>>

%
<<kintroptions, echo=FALSE>>=
knitr::knit_hooks$set(render_sweave())
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  fig.width = 6,
  fig.height = 4,
  fig.pos = 'H',
  prompt=TRUE
)
options(prompt="R> ")
@
%

@@

The \pkg{disaggregation} package contains a C++ function that defines the model and computes the joint likelihood as a function of the parameters and the random effects, in the format expected by \pkg{TMB}. The \pkg{TMB} package then calculates estimates of both parameters and random effects using a Laplace approximation. Evaluation of the objective function and its derivatives is performed via \proglang{R}.
